Reading Notes

### 2020-07-20 reading-notes.tex
reading about CG lipid bilayers

\cite{Shelley2001}

>>>>

\cite{Shelley2001}
CG model for phospholipids. parameterized to mimic structural properties--which ones? they were fit to bond distributions (algorithm sounds like IBI but they don't say IBI... anyway it's iterative based on Boltzmann inverse of RDF)
reproduces structure of bilayer--property that was not directly fit. The initial configuration was random. 
how do they verify that it reproduces the bilayer? rdfs, density maps, also snapshots.
